% !TeX program = xelatex
% Run with XeLaTeX

\documentclass[]{richard-dang}

\begin{document}
\pagestyle{empty} %to remove the page numbers
 \renewcommand{\labelitemi}{$\diamond$}


\header{Richard}{Dang}
{University of Waterloo} {- Computer Engineering}
{{\faMobile \hspace{\FAspace} (647) 717-0339 
\sep \faEnvelope \hspace{\FAspace}
\href{mailto:richardspacedang@gmail.com}{richardspacedang@gmail.com}
\sep \faSearch \hspace{\FAspace}
\href{http://richarddang.com}{richarddang.com}
\sep \faGithub \hspace{\FAspace}
\href{https://github.com/Richard-Dang}{Richard-Dang}
\sep \faLinkedinSquare \hspace{\FAspace} 
\href{https://linkedin.com/in/dangrichard}{dangrichard} 
}}
 
% \section*{\faDashboard \hspace{\FAspace} SKILLS}
\section*{SKILLS}
\medbreak
\begin{tabularcv}
        &  \worktitle{\textbf{LANGUAGES}\hspace{5.6mm}}{Java, Python, JavaScript, Scala, SQL, HTML and CSS }
        \\
        &  \worktitle{\textbf{TECHNOLOGIES}}{Spark, Kafka, AWS EMR/S3, Hortonworks, Docker, Maven, Jenkins, Git and JetBrains}
        \\
        &  \worktitle{\textbf{CONCEPTS}\hspace{8mm}}{Distributed Systems, OOP, REST API, CI/CD and Agile}
\end{tabularcv}   

% \section*{\faGroup \hspace{\FAspace} EXPERIENCE}
\section*{EXPERIENCE}
\medbreak
\begin{tabularcv}
    Sep. – \newline 
    Dec. 2019   &  
                    \href{https://www.nerdwallet.com}{
                    \worktitle{Data Engineering}{Nerdwallet  ---  San Francisco, CA}}
                    \begin{tabitemize}
                        \item Created \textbf{Spark streaming} app to enrich traffic events at \textbf{6400 events/sec} from Kafka to S3
                        \item Developed near real-time streaming app that groups events into sessions based on user inactivity
                        \item Used Spark \textbf{batch processing} to detect and categorize bot activity in event traffic on a daily basis
                        \item Set up cluster infrastructure for \textbf{Kafka} and \textbf{AWS EMR} to host Spark applications
                    \end{tabitemize} 
                    \\[\vspacepar]\\[\vspacepar]
    Sep. – \newline 
    Dec. 2018   &  
                    \href{https://www.ultimatesoftware.com}{
                    \worktitle{Big Data Engineering}{Ultimate Software  ---  Weston, FL}}
                    \begin{tabitemize}
                        \item Developed \textbf{Spark} apps for event ingestion and GDPR which processes over \textbf{600 events/sec}
                        \item Built a \textbf{Spark streaming} app for processing and replaying events with \textbf{Kafka} integration
                        \item Setup \textbf{Hadoop} on a \textbf{Docker} environment for automated integration testing through \textbf{Concourse}
                        \item Integrated metrics instrumentation using \textbf{AOP} allowing for greater insights on app performance
                    \end{tabitemize} 
                    \\[\vspacepar]\\[\vspacepar]
    Jan. – \newline 
    Apr. 2018   &  
                    \href{https://www.ultimatesoftware.com}{
                    \worktitle{Software Engineering}{Ultimate Software  ---  Toronto, ON}}
                    \begin{tabitemize}
                        \item Introduced functionality to host web app used for managing time clocks with \textbf{Spring} and \textbf{Hibernate}
                        \item Created GDPR app to purge deleted employees by implementing schema constraints to maintain database integrity using \textbf{Liquibase}
                        \item Incorporated supervisor override check-in feature on web time clock app using \textbf{AngularJS}
                    \end{tabitemize} 
                    \\[\vspacepar]\\[\vspacepar]
    May – \newline 
    Sep. 2017   &  
                    \href{http://hubdoc.com}{
                    \worktitle{Software Developer}{Hubdoc  ---  Toronto, ON}}
                    \begin{tabitemize}
                        \item Built and migrated hundreds of document fetching services, increasing reliability from \textbf{46\%} to \textbf{73\%}
                        \item Implemented an intranet dashboard with \textbf{ExpressJS} and \textbf{BackboneJS} used for proxy management
                    \end{tabitemize} 
                    \\[\vspacepar]\\[\vspacepar]
    Sep. – \newline 
    Dec. 2016   &   
                    \href{http://flipp.com}{
                    \worktitle{Associate QA Analyst}{Flipp  ---  Toronto, ON}}
                    \begin{tabitemize}
                        \item Introduced continuous integration across multiple projects providing early risk detection, feedback loops, and quick deployments utilizing \textbf{Jenkins}
                        \item Automated performance testing to ensure response times for A/B test framework using \textbf{JMeter}
                    \end{tabitemize} 
    % Jan. – \newline 
    % Apr. 2016   &   
    %                 \href{http://geosemi.com}{
    %                 \worktitle{Software Test and Tools Developer}{GEO Semiconductor  ---  Toronto, ON}}
    %                 \begin{tabitemize}
    %                     \item Reduced overall testing time by more than \textbf{80\%} through automation of testing procedures
    %                     \item Developed host tools for internal testing/development and designed regression test plans
    %                 \end{tabitemize} 
\end{tabularcv}   

% \section*{\faStar \hspace{\FAspace} PROJECTS}
\section*{PROJECTS}
\medbreak
\begin{tabularcv}
    Feb. - \newline 
    May 2018   &   
                    \href{https://github.com/Richard-Dang/FindMyResume}{
                    \worktitle{Find My Resume}{Angular 4, Spring Boot and Heroku}}
                    \begin{tabitemize}
                        \item Web app that hosts a collection of resumes which users can be preview, edit and download
                    \end{tabitemize} 
                    \\[\vspacepar]\\[\vspacepar]
    Jul. -  \newline 
    Nov. 2016   &   \href{https://github.com/Richard-Dang/AlexaBuddy}{
                    \worktitle{Alexa Buddy}{Python, Flask-Ask, Indico API and Reddit API}}
                    \begin{tabitemize}
                        \item Amazon Alexa app that responds with Reddit posts while filtering out negative sentiment
                        \item Won \textbf{\href{https://devpost.com/software/alexabuddy}{Best Hack Against Online Harassment}} at Electric City Hacks
                    \end{tabitemize} 
                    \\[\vspacepar]\\[\vspacepar]
\end{tabularcv}   

% \section*{\faMortarBoard \hspace{\FAspace} EDUCATION}
\section*{EDUCATION}
\medbreak
\begin{tabularcv}
    2015 - \newline 
    Apr. 2020 (expected)   &   
                    \worktitle{Computer Engineering (Bachelor of Applied Science)}{University of Waterloo}
                    \begin{tabitemize}
                        \item Distributed Computing, Data Structures and Algorithms, Algorithm Design and Analysis, Database Systems, Programming for Performance, Computer Networks, Computer Security, Operating Systems, and Compilers 
                    \end{tabitemize} 

\end{tabularcv}

\end{document}